\section{Responsibility I see in my Leadership}

% Drive a vision, to stiere actions! Don't do the actions.
% Delegate, and Accountablity
% Vision max vs. Input max

%-> 3 Years: A more challeging Range! Onto the NEW, NEW Thing

\subsection{Drive a Vision}
\paragraph{Set a path}
A leader's primary responsibility is to find, set and drive a compelling vision that aligns with the organization's goals or sets them.
This vision serves as a beacon, guiding the team towards a shared future and inspiring them to work together with purpose and enthusiasm.
A clear and constant vision helps prioritise efforts and align individual contributions with the broader objectives inside and outside the team.

\paragraph{Definition of a Vision}
A vision is a future state that can be expressed as a sentence, a picture, or a goal.\\

It doesn't need to be explicitly defined in detail. Explanations can be provided if they help or are necessary in the decision-making process. However, it should be a vital part to guide action and strategy.
It is not a strategy or a plan for achieving it! In the literature, you can find distinctions between a vision and a mission statement, but the goal is to make it as simple as possible: so that it can affect decision-making today, and can be an integral part of a team or company.\footnote{
	For example, a vision can be expressed as a \textit{state} to be in, which could fall more under the category of a mission statement: \textit{Wir sind ein leistungsstarker digitaler Betrieb}. This typically indicates a mission statement rather than a vision statement. However, in this context, there is no difference.
}\\

A vision may have two parts: an internal and an external outlook. For example, \textit{Wir sind ein leistungsstarker digitaler Betrieb} and \textit{Zuverlässig $\&$ aktuell informiert: So bewegen wir München}. These two parts combined can also be a vision for a company.\\

The responsibility lies in ensuring this vision is constantly upheld and remains an integral part of the team, influencing decisions.\footnote{
	Projects, strategies, daily discussion.
}


\paragraph{Motivate Internally and Externally}
Ensuring social support, capital, and information input for the team to achieve the vision is also part of the leader's responsibility.

\paragraph{Knowing the difference}
If a vision has a whidely accepted goal\footnote{
	This means, it's understood, can be whidley evaluated in the same way, and or can 
}

\subsection{Information Integration}
\paragraph{Alignment}
Leaders must adeptly gather, integrate, and analyze information from various sources. This information should then be used to evaluate progress against the vision or strategy and to constantly communicate what it takes to align actions to achieve it internally and externally.

\paragraph{Take the left over decisions}
"Left decision" refers to those crucial choices that are "two-door" decisions, meaning they may have a significant impact and are not quickly reversible. If no analytical, logical, or group consensus can be reached for these decisions, leaders must take responsibility and make them.

\paragraph{Delegation and Accountability}
Delegation is crucial for effective execution. Leaders must trust their team members with responsibilities while holding them accountable for outcomes. This empowers the team and allows leaders to focus on strategic priorities. The difference between micromanagement and effective delegation lies in giving team members the autonomy to execute tasks while providing support and oversight as needed.



\paragraph{***Finding great Teammates for great Teammates}
%TODO Loser Einschub

% The goal is not, that they learn from me, that they learn from the great team mates!


% Refactoring II

%% Tools
%%%Vision (Output) Maximizing

%%%Team (Input) Maximizing

Until now, I did this. With the given input, to reach a certain goal. However, if the input was not sufficient, then the goal was adjusted.

Bei größeren Zielsetzungen und größeren Verantwortung, birgt die die Input Maximizierung Probleme.

... Probleme
Colleges Bases: The risik is, that it can be demortiliseing, pull und pushing other people. Not everybody has the patents for it.

More work has to pick up by other team mates

And you as a leader don't hourner the commitment each teammember made to the vision, by allowing team dynamcis or not sufficent teammembers dafür sorgen, dass die Zielbereitschaft andere Teammitglieder nicht erreicht wird.


... Meine Führungsverantwortung:
Mein Versprech

Personen geben sich der Vision und Erreichugn hin (für diese Personen habe ich ebenso verantwortung); Wenn Mehrlast auf Personen fällt, welche Teile des Team zu langsame für die gegeben Herausforderungen sind, liegt hier ebenso die Verantwortung bei mir.


Bei größeren Strategien Zielsetzungen, liegt jetzt hier die Priorität (Lernen, die zu tun.)
Mehr auf Vision Maximizerung.

Die besten für die besten finden!


% Refactoring I
Der Schwere Teil: Entscheidungen für das Team, die Vision und Kunden treffen. Kein eigener Standard setzen.
- Entscheidung in den ersten Wochen: 
- Kontinuierlich: Commitment der Teammitglieder wertschätzen, wenn der Einsatz von ihnen dadurch geschältert ist, oder sie auch nicht die Vision erreichen.
- Neue Strategie, welche der Vision näher kommt;Neue Capacitäten werden benötigt. Selbst durch Loyalität muss dann ein transit gefunden werden.
- Low Performance Part vs Priorsierung von Ressourcen; Es ist nicht nötig, nur low Performance zu entlassen.

Bisher war es so, dass ich mit dem geradbeit habe, was da war und gegebenfalls meine Vison/ Strategie angepasst habe (nach unten korrigiert).
Jetzt bin ich verantwortlich für das Team, dass die Vsion erreicht wird, und den Input wähle ich aus und pflege ihn.

Deletegat, accountability, quality: Integrate Team results (Zu einander bounces); 
What does it mean, to mean great. Is very abitray.


Continuosly keep it great

The aspekt is to make Continuuesly Assembe a great team for the vision.

—-

%%%% Refactoring





Finding talentent people, who will de

maybe given a more true statement.
——
What I do, is using the talent a got in the best possible way. 
There is a way, if the vision requires cabbilities, which are not here anymore.

Make a cut, as quick as possible!
Loyatcly. 

There is a difference between the zielzustand.

Making a quick decision - Couple weeks, less then a month.

There are here for me, I‘m there for them.

If the vision evolves or the required stategy cabaility are increasing, then a discussion needs to be.


The loc

First, we are here for other to archive the vision. By doing it we bond over it, by creating something great.

What to do, if cabilities are not sufficient after a certain time. 
The vision and the goal dictates.
Responsibility to make decisions 
Horner the commitment of the team, of there commitment to the vision and enshojsdofias.
for the team, there commitment to the vision and 

Maybe category of quality.
There is then a lower cabinet part of the team as well. 
this ranking, determine the priority and resource investment.

Make the investment Gebern, bewusst, wo die Priorität liegt.
Ebenso, kann auch die Entscheidung getroffen werden, nicht jemand weiter zu führen im Team, weil die Ressourcen für andere Themen oder Personen aufgewandt werden müssen, im Bezug für Visoin.

Meine Persönlichkeit erlaubt mir nicht, anhand eines persönlichen Standard, Selectionsentscheidungen zu treffen.
Die 

Eine eigenen Einschätzung ist das hier.
Diese Einschätzung kann dann bewertet werden.
Sicherlich, nicht alle Punkt, die anderen einfallen werden hier aufgefasst. 
Was hier aufgefasst ist, sind die Punkte, welch für mich ein bewussteren Anspruch erfordern. Dinge, welche hier nicht erwähnt sind, wo automatische Verhaltsweise ausreichen oder automatisch kommuniziert werden.


\subsection{Essenble a Great Team}
Building a strong and capable team is essential for successful leadership. This involves recruiting talented individuals who possess the skills, experience, and mindset needed to achieve the vision.


\paragraph{To be great, what does it mean?}
In relation to the overall topic of this, it means accomplishing things that are relevant for a great number of people.

Being great in this context does not necessary mean having a great number of skills, which may accomplish something. Nonetheless, having a great skillset may be an indicator of achieving great things in the future.

The responsibility I see is to find people who have indicated or already proven that they are capable of achieving great things. This is relevant for the team itself, to have team members from whom to learn, strive, and be pushed by.


\paragraph{The Risik}
If the vision is not clear and what it takes to achieve it is not thought out—whether in terms of team capabilities or strategy—then assembling a team is risky. The team may not move in the direction of the vision, and the selected skillset may not be complementary.


If they may do great things, does not absolve the need for a clear vision and executional strategy,  it may mean, that a the team is doing great thing \textit{dispite a leadership}.


\paragraph{What to promote}
Finding the right balance between providing freedom and learning from the best is crucial. Leaders should create an environment where team members have the autonomy to explore and innovate while also learning from experienced mentors and established best practices. 


\paragraph{Feedback and Excellence}
Regular feedback is essential for continuous improvement and achieving excellence. Leaders should create a culture where feedback is constructive, timely, and focused on growth. Recognizing and celebrating excellence motivates the team to strive for high standards.

\paragraph{Commitment to Leading the Team}

\subsection{Environment to find the best solutions}
Creating an environment that encourages finding the best solutions is a core leadership responsibility. This involves fostering open communication, promoting collaboration, and encouraging diverse perspectives.

\paragraph{Memo}
Using memos effectively can help communicate important information, updates, and decisions to the team. Clear and concise memos ensure everyone is informed and aligned, facilitating better decision-making and coordination.

\paragraph{Style of group discussion}
The style of group discussions can significantly impact the quality of solutions. Leaders should encourage open, respectful, and constructive discussions where all voices are heard. This collaborative approach helps surface diverse ideas and fosters innovation.

\subsection{Execution}
Executing the vision and strategies effectively is a critical leadership responsibility. This involves turning plans into action, ensuring that the team is aligned and resources are optimally utilized.

\paragraph{Take the left decision}
Making the tough, sometimes unconventional decisions is a key aspect of leadership. These "left decisions" often require courage and foresight, as they might deviate from the norm but are necessary for progress and innovation.

\paragraph{Push, to make more possible}
Leaders should constantly push the boundaries of what is possible. This involves challenging the status quo, encouraging the team to stretch their limits, and fostering a culture of ambition and perseverance. By pushing for more, leaders drive continuous improvement and inspire their teams to achieve greater heights.

\paragraph{Lose* Personal Guide Finding Value}


So, the topic is called: Finding Value!
Inset of finding the opertunities with the greates marginal value for satificfation. (This can by strategy power, but it can also be just temparary satification. Then again, an other operturnity can arrise, which has a high margina emotional value)

Two guiding this:
- Find value, where the margial satification rate is very high. 
- Then Delegat & Accountablity, lead team to develop X to give person or a group the strategy power.
Note: This is different, from a system, which very body just have to fill in and "bedinen". For example. Urlaubsplanung: This is a system (Exeption can be made), that has no stratgy power for somebody. Therefore no satifaction feeling. Then the accosition is, that I provided this statgy power for them.

I'm not also relevant for quick relevae.

Strategy Power, to allow other to have strategy power


\subsection{Context}
Es soll nicht vollständig sein.
Das Ziel soll sein, dass es koheränt und verständlich ist.

\subsection{Extention}


\paragraph{****Relationship to Strategy: Be Nimble}
The tool of choice would be a strategy to point the way.\\

A vision is just a future state. Normally, there is no path shown that ensures a team today can move towards this vision state in the future. 

A strategy would not only be a path from today to the vision itself, it would also be relisation, how this vision would look like. Sort of in the same way, as objects and key results interact with each other. A object is just a goal. The key results are mostly definied not derived indicator of this objective. In similar means, definies a strategy $"$a$"$ expression of the vision.

----
Even so, some of the vision statements can mostly not be 

To align futher desicio

% There is only now! And ever will be!

% Likeleyhood: To estimate, what comes next. Prediction the next words. The problem is, that if you are not testing your feeling, if you thought, that you could predict, what comes next

% A Vision is a theortical model of the world!
% This model, does not exist (Invetion or Discovery of mathematics). It even does not exist on pages.
% The goal is, to make prediction about the world.

The goal is, that other people re

Organsiting Schema: Aling ressource

A strategy may be the first realization of the vision.


For example, YouTube's mission statement is \textit{to give everyone a voice and show them the world} and Alphabet \textbf{4Es: Earn, Entice, Expand, Experiment} is it's current stategy. However, there is no single strategig realization of this vision. It is the first  
...
Instead, various strategies must be implemented and adapted to work towards achieving it.

As circumstances change, leaders must continuously reassess and update the strategy to ensure it remains coherent and aligned with the set vision. Regularly updating the strategy is essential to keep the team focused and adaptive in a dynamic environment. However, this does not mean that the vision has to change. It indicates that the path or expression of the vision may need to be adjusted.

\paragraph{Knowing the difference: Vision Max or Team Max}
There is a difference, between maximizing vision or maximising the input.

What is meant by that is, maximizing the vision is, constantly finding and keeping the best team member and ressources to strive to the vision. The focus is to doing everything to position the team or fulliel the vision, and not lowering any standards. On the other hand, \textit{maxizing the input} with thegiven ressource and teammember cabailities the best relesation of the vision will be strived at.

The responsiblity lies in that, know the own capacity to understand, what principial can be applied. The assumeion is, that follow the one or other prinzipal is not a consiuse choose, but rather a behavior for ever endover. However, I knowing the capacity or whishing to change it, is important for setting the vision or subgoals and in communicating this to the team and letting new person know, what to expect.

For example: If maximizing a personal teammembers potential is not suffient to achive ,


There is a different responsiblity: Honouring the commitment, other teammember made to the vision including the archivment of the strategiy great things.




